---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
```{r loadData}
library("readr")

data<-read_csv("activity.csv")
```

## What is mean total number of steps taken per day?
```{r meanDaySteps}

library("dplyr")
library("lattice")

data1 <- data %>% group_by(date) %>% summarize(daysteps = sum(steps))

histogram(data1$daysteps, data=data1, xlab='Daily Steps')
meanDailySteps = mean(data1$daysteps, na.rm = T)
medianDailySteps = median(data1$daysteps, na.rm = T)
```

## What is the average daily activity pattern?
```{r dailyPattern}
library('ggplot2')

#data2 <- data %>% group_by(interval) %>% summarize(daysteps = mean(steps, na.rm = T))
data2 <- aggregate(data$steps, by = list(data$interval), mean, na.rm=TRUE)
ggplot(data2, aes(x = interval, y = steps)) + geom_line()

```

## Imputing missing values
We use mean for the corresponding time interval to fill out the missing values. The new dataset, called fullData holds the upddated data.

```{r MissingValues}

missingValues <- data %>% filter(is.na(steps))
number_missValues <-length(missingValues$steps)

fullData <- data
fullData$steps[is.na(fullData$steps)] <- 
    tapply(fullData$steps, fullData$interval, mean, na.rm = TRUE)

histogram(fullData$steps, data=fullData, xlab='Daily Steps')
```

## Are there differences in activity patterns between weekdays and weekends?
``` {r weekdays}

fullData$Day <- weekdays(as.Date(as.character(fullData$date)))
fullData$DayType <- as.factor(c("Weekend","Weekday"))

weekendDays <- fullData$Day == "Saturday" | fullData$Day == "Sunday"

fullData$DayType[weekendDays] = "Weekend"
fullData$DayType[!weekendDays] = "Weekday"

fullData2 <- tapply(fullData$steps, 
                        list(fullData$DayType, fullData$interval),
                        mean)

x <- as.data.frame(as.table(fullData2))
names(x) <- c('DayType', 'Interval', 'Steps')

xyplot(Interval ~ Steps | DayType, x)
```